Testable normative theories

### 2020-05-01 simple.tex
Corr irrefl ⇒ asymm

\begin{definition}[No self-attack]
	$\gbeats$ must be irreflexive.
\end{definition}

@@

>>>>

\begin{definition}[No self-attack]
	$\gbeatsstar$ must be asymmetric.
\end{definition}

\begin{definition}[No repetition]
	$\nexists \ar_0 \in \gargs[\phi], \ar_1 \in \allargs, \ar_2 \in c(\ar_0) \suchthat \ar_2 \gbeats \ar_1 \gbeatsstar \ar_0$.
\end{definition}

@@

\begin{remark}
	When $\gbeatsstar$ is as defined above, asymmetry of $\gbeatsstar$ with the other conditions implies No repetition: by construction of $\gbeatsstar$, $\forall \ar_0 \in \gargs[\phi], \ar_1 \in \allargs, \ar_2 \in c(\ar_0) \suchthat \ar_2 \gbeats \ar_1: \ar_0 \gbeatsstar \ar_1$, thus, by asymmetry, $¬(\ar_1 \gbeatsstar \ar_0)$.
\end{remark}
